A content-sensitive framework for modeling episodic memory reveals event-like structure in naturalistic experience, recall, and neural processing

### 2019-08-25 paper/main.tex
recompiled docs with fixes

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/eventseg}
\caption{\small \textbf{Modelling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].  \textbf{A.} Topic vectors ($K = 100$) for each of the 1976 video timepoints.  \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.  Event boundaries detected by the HMM are denoted in yellow (34 events detected).  \textbf{C.} Average topic vectors for each of the 34 video events. \textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video.  \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D. Event boundaries detected by the HMM are denoted in yellow (27 events detected).  \textbf{F.} Average topic vectors for each of the 27 recalled events from the example participant.  \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).  For similar plots for all participants see Figure~\matchmats.  \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).  To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).  The heat maps in each panel were created using \texttt{Seaborn}~\citep{WaskEtal16}.}
\label{fig:model}
\end{figure}

>>>>

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/eventseg}
\caption{\small \textbf{Modelling naturalistic stimuli and recalls.} All panels: darker colors indicate greater values; range: [0, 1].  \textbf{A.} Topic vectors ($K = 100$) for each of the 1976 video timepoints.  \textbf{B.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel A.  Event boundaries detected by the HMM are denoted in yellow (36 events detected).  \textbf{C.} Average topic vectors for each of the 36 video events. \textbf{D.} Topic vectors for each of 294 sentences spoken by an example participant while recalling the video.  \textbf{E.} Timepoint-by-timepoint correlation matrix of the topic vectors displayed in Panel D. Event boundaries detected by the HMM are denoted in yellow (37 events detected).  \textbf{F.} Average topic vectors for each of the 37 recalled events from the example participant.  \textbf{G.} Correlations between the topic vectors for every pair of video events (Panel C) and recalled events (from the example participant; Panel F).  For similar plots for all participants see Figure~\matchmats.  \textbf{H.} Average correlations between each pair of video events and recalled events (across all 17 participants).  To create the figure, each recalled event was assigned to the video event with the most correlated topic vector (yellow boxes in panels G and H).  The heat maps in each panel were created using \texttt{Seaborn}~\citep{WaskEtal16}.}
\label{fig:model}
\end{figure}
